\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}

% Put a motivation for a research topic here.
Because of my part-time job in the Erasmus MC, I have seen a lot of medical devices, most of them have one or more embedded systems inside of them. Because of my interest both for embedded systems- and the medical world, I wanted to find a graduation project where both fields came into play. In the Erasmus MC I found Caitlin Ramsey, which did her PhD in the field of contact-less vital signs monitoring of neonates using mmWave radar technology. Caitlin was looking for someone to research the ability to do the vital signs calculations on the chip hardware itself, where currently it was done using post-processing techniques. I was immediately interested in this topic, and after I found Marco Zuniga as my thesis supervisor from the TU Delft, I was ready to get started.

\vspace{1\baselineskip}

I want to thank all the persons that have helped me complete my graduation project. First of all, a special thanks to Caitlin for her great support during this project. I could always come to you with any questions I had, and you always answered them in great detail, both technical questions and more general questions. My thesis would not have succeeded without you. Also a big thanks to Marco. You were always able to keep an overview of the project, and helped me approach the project in an academic way. In moments of doubt, you were a great help to steer me in the right direction and to make the project as enjoyable for me as possible. I also want to thank all of the persons which helped me validate the project. Thank you for your time and patience while sitting very quietly in a chair for 5 minutes. I also want to thank all of the people who supported my along the way. Without your kind and encouraging words, I would have probably stranded somewhere halfway. In that regard, a special thanks to Geeske. You have always been there for me, by celebrating successes, and by cheering me up in difficult times. You always gave me the energy to push through and finish with a great result. 

\vspace{1\baselineskip}

\reportAuthor

\vspace{1\baselineskip}

\noindent
Delft, The Netherlands

\noindent
\today